Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes.

### 2020-04-04 Ben_Manuscripts/hdphmm/Outline.tex
New figures and updates to outline

  %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
  Using the IHMM framework, we estimated the most likely number and sequence of hidden
  states in each solute center-of-mass trajectory while simultaneously inferring VAR(1)
  parameters for each state and the overall state transition probability matrix, $T$.
  \begin{itemize}
    \item We created a python implementation of this process which we heavily adapted from
    the MATLAB code of Fox et al.~\cite{fox_sticky_2007} 
    %BJC3: I got the software from this page: https://homes.cs.washington.edu/~ebfox/software/
    % Maybe I should reach out to emily fox to see how she would prefer I cite the software?
    %MRS3: be a bit more specific about what the criteria were for convergence.
    %BJC3: See if that's better
    \item Parameter estimation is iterative. Therefore, we looked for convergence 
    of each entry in the $c$ vector as well as the $A$ and $\Sigma$ matrices of 
    Equation~\ref{eqn:var}.
    \item Plots illustrating parameter convergence are available in the SI.
    \item We refer the interested reader to much more extensive descriptions of 
    %MRS3: be more specific about which parts from the above are in the references
    %BJC3: made more specific
    the inference and sampling procedures used to estimate the VAR(1) parameters
    and the state sequence. 
    ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
  \end{itemize}

@@

  We start by applying the IHMM algorithm to 3D solute center-of-mass coordinate 
  trajectories transformed relative to the closest pore center.
  \begin{itemize}
    \item We tracked the solute's motion along the pore axis with the center-of-mass
    $z$ coordinate.
    \item Using the nearest pore center as the origin, we represented the radial 
    distance of each solute's center-of-mass from the pore center in 2 dimensions,
    $x$ and $y$ (see Figure~\ref{fig:cartesian_cylinder}).
    %MRS3: I'm not following the below? I don't know that we WANT to find more states, in my mind doing it this way 
    %the math is simpler this way since we don't have to rewrite things in term of radial diffusion
    %MRS3: we can brainstorm this as needed!
    \item By using 2 dimensions, rather than a single radial dimension, we
    increase the likelihood of finding more states since a single radial
    mean can be represented by an infinite number of $x$ and $y$ coordinate combinations.
  \end{itemize}

@@

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{eqn:var}.
  \begin{itemize}
    \item The entries of $A$ and $\Sigma$ do not vary over a wide range, so
    the final parameters were relatively insensitive to the priors.
    \item In order to maximally automate the IHMM procedure, we attempted to
    parameterize the prior on $\mathbf{c}$ in an intelligent way.
    \item The prior parameters should be chosen such that the means of 
    each state lie within a region of reasonable probability of the prior (see
    Figure~\ref{fig:prior_guesses}).
    \item In each dimension, we defined the prior mean to lie halfway between the 
    maximum and minimum of each trajectory dimension. 
    \item To parameterize the prior's variance in each dimension, we defined the
    maximum and minimum to be 2 standard deviations from the prior mean.
    \item Although this approach has worked quite well for the data in this work,
    it is important to check the results to determine whether further adjustments
    to the prior might be needed.
    \item In the Supporting Information, we show the result of a parameterization
    where the prior parameters of $c$ were poorly chosen. %TODO
  \end{itemize}

@@

  % BJC2: It's probably possible to convert to from x, y, z to r, z but
  % I need to figure out the transformation of A. This approach works though.
  We reparameterized the time series, preserving the state sequence, in terms
  of the radial and axial coordinates ($r$, $z$) because $x$ and $y$ aren't 
  meaningful alone due to the system's radial symmetry.
  % the mean in $r$ is a useful clustering variable.
  \begin{itemize}
    \item It will also be clearer to analyze the final parameter set in
    terms of $r$ rather than $x$ and $y$.
    \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
%    \item In order to keep the same states found when we applied the algorithm
%    in 3D, we reapplied the IHMM to the cylindrical trajectories with a fixed 
%    state sequence, only allowing inference on the VAR(1) parameters.
    %MRS3: would it be clearer to say you appplied only the inference part of the process on the clustered data?
    %BJC3: like this?
    \item We fixed the state sequence from the 3D parmeterization and applied the
    inference component of the IHMM procedure to the cylindrical trajectories in
    order to estimate the VAR(1) parameters in terms of $r$ and $z$.
  \end{itemize}

  We clustered like parameter sets in order to reduce the state space to
  a more easily interpretable size.
  \begin{itemize}
  \item For each solute studied, we identified 200-300 independent states, each
  with separate VAR(1) parameters. % BJC2: just a guess for now
   \item Many of these states exhibit very similar dynamical behavior except their
   mean levels are different, especially in the axial direction where solutes could
   get trapped along a broad and continuous range of $z$ coordinates.
   \item Since we do not know the number of states with shared dynamical behavior
   beforehand, we used a non-parametric Bayesian Gaussian mixture model in order
   to cluster them. % cite scikit-learn  
%   \item This is necessary for us to perform any kind of mechanistic speculation.
  \end{itemize}

  % BJC2: this part may expand a bit if I try different clustering approaches. But
  % this is the one I'm going with for now.
  We clustered based on 5 variables: the radial means of each state, the two
  eigenvalues of $A$ and the two eigenvalues of $\Sigma$.
  \begin{itemize}
   \item Unfortunately, the number of independent parameter sets is too low for
   clustering in higher dimensions. 
   \item Ideally, we could use all of the entries of $A$ and $\Sigma$ in addition to 
   the radial means.
   \item It would not be helpful to use the means in the $z$ direction because solutes
   are essentially unbound in that direction.
   \item However, in our previous work, we observed radially dependent dynamical 
   behavior.~\cite{coscia_chemically_2019}  % cite new paper eventually too.
  \end{itemize}

@@

  %MRS3: ``used the IHMM algorithm'' -> ``used the parameter inference part of the IHMM algorithm''?
  We used the parameter inference component of the IHMM algorithm in order to 
  infer $A$ and $\Sigma$ of the clustered states.
  \begin{itemize}
   %BJC2: I'm unsure of the precise reasoning here.
   \item We could not simply take the mean of the clustered 
   $A$ and $\mathbf{e}_t$ parameters because it is not clear that this is a linear 
   operation for this problem. 
   \item To circumvent this problem, we modified the ($r$, $z$) solute
   trajectories so that they had a mean of zero, leaving only the 
   fluctations. 
   \item We did this by subtracting the maximum likelihood estimate
   of the $\mathbf{c}$ vector from each same-state segement of the unclustered
   trajectory.   
   \item We used the IHMM algorithm on this modified trajectory to infer
   the clustered state parameters by fixing the clustered state sequence. 
  \end{itemize}

@@

  \section{Results and Discussion}
  %MRS2: how stable are the results to realizations of the system
  \subsection{Inferring Solute Transport Mechanisms}

  Clustering parameters sets results in X distinct dynamical modes.
  \begin{itemize}
    \item In the figure below, we show time series simulations that qualitatively
    illustrate the difference in dynamical behavior between modes.
  \end{itemize}

  %BJC1: a figure showing some representative fluctuations in each mode

  \noindent We can relate the identified states back to transport mechanisms.
  \begin{itemize}
  	\item More detailed discussion of identified states
  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
  	\item How do these states compare to those identified in our previous work?
  	\item Any new states?
  \end{itemize}

@@

  \noindent Trajectory realizations qualitatively match MD simulation trajectories.

  \begin{itemize}
    %MRS2: think about how to quantify the simiilarity of the hopping and trapping behavior.
    \item Look for hopping and trapping behavior
  \end{itemize}

  \noindent MSDs generated from stochastic trajectories match those from MD.
  \begin{itemize}
    %MRS2: again, think about the best ways to quantify similar between MD and stochastic trajectories.
  	\item Look at curvature and 1-$\sigma$ confidence intervals
  \end{itemize}

@@

  \noindent We can predict macroscopic flux and selectivity.
  \begin{itemize}
  	\item Flux as function of pore length
  	\item Selectivity as function of pore length (if flux scaling is length-dependent)
  \end{itemize}

@@

@@

  \noindent We can use the IHMM to predict macroscopic transport properties. \\

  %MRS2: below probably doesn't need to be stated?
  \noindent The IHMM is not limited to the H\textsubscript{II} phase.

>>>>

  %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
  Using the IHMM framework, we estimated the most likely number and sequence of hidden
  states in each solute center-of-mass trajectory while simultaneously inferring VAR(1)
  parameters for each state and the overall state transition probability matrix, $T$.
  \begin{itemize}
    \item We created a python implementation of this process which we heavily adapted from
    the MATLAB code of Fox et al.~\cite{fox_sticky_2007} 
    %BJC3: I got the software from this page: https://homes.cs.washington.edu/~ebfox/software/
    % Maybe I should reach out to emily fox to see how she would prefer I cite the software?
    %MRS3: be a bit more specific about what the criteria were for convergence.
    %BJC3: See if that's better
    \item Parameter estimation is iterative. Therefore, we looked for convergence 
    of each entry in the $\mathbf{c}$ vector as well as the $A$ and $\Sigma$ matrices of 
    Equation~\ref{eqn:var}.
    \item Plots illustrating parameter convergence are available in the SI.
    \item We refer the interested reader to much more extensive descriptions of 
    %MRS3: be more specific about which parts from the above are in the references
    %BJC3: made more specific
    the inference and sampling procedures used to estimate the VAR(1) parameters
    and the state sequence. 
    ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
  \end{itemize}

@@

  We start by applying the IHMM algorithm to 3D solute center-of-mass coordinate 
  trajectories transformed relative to the closest pore center.
  \begin{itemize}
    \item We tracked the solute's motion along the pore axis with the center-of-mass
    $z$ coordinate.
    \item Using the nearest pore center as the origin, we represented the radial 
    distance of each solute's center-of-mass from the pore center in 2 dimensions,
    $x$ and $y$ (see Figure~\ref{fig:cartesian_cylinder}).
    \item By working in cartesian coordinates, we avoid mathematical complexity
    introduced by cylindrical coordinates while estimating the state sequence.
  \end{itemize}

@@

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{eqn:var}.
  \begin{itemize}
    \item The entries of $A$ and $\Sigma$ do not vary over a wide range, so
    the final parameters were relatively insensitive to the priors.
    \item In order to maximally automate the IHMM procedure, we attempted to
    parameterize the prior on $\mathbf{c}$ in an intelligent way.
    \item The prior parameters should be chosen such that the mean level of 
    each state lies within a region of reasonable probability of the prior (see
    Figure~\ref{fig:prior_guesses}).
    \item In each dimension, we defined the prior mean to lie halfway between the 
    maximum and minimum of each trajectory dimension. 
    \item To parameterize the prior's variance in each dimension, we defined the
    maximum and minimum to be 2 standard deviations from the prior mean.
    \item Although this approach has worked quite well for the data in this work,
    it is important to check the results to determine whether further adjustments
    to the prior might be needed.
    \item In the Supporting Information, we show the result of a parameterization
    where the prior parameters of $c$ were poorly chosen. %TODO
  \end{itemize}

@@

  We reparameterized the time series, preserving the state sequence, in terms
  of the radial and axial coordinates ($r$, $z$) because $x$ and $y$ aren't 
  meaningful alone due to the system's radial symmetry.
  \begin{itemize}
    \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
    \item We fixed the state sequence from the 3D parmeterization and applied the
    inference component of the IHMM procedure to the cylindrical trajectories in
    order to estimate the VAR(1) parameters in terms of $r$ and $z$.
  \end{itemize}

  We clustered like parameter sets in order to reduce the state space to
  a more easily interpretable size.
  \begin{itemize}
  	\item For each solute studied, we identified 200-325 independent states, each
   	with separate VAR(1) parameters.
   	\item Many of these states exhibit very similar dynamical behavior except their
   	mean levels are different, especially in the axial direction where solutes could
   	get trapped along a broad and continuous range of $z$ coordinates. 
  \end{itemize}

  We reduced the parameter space used agglomerative clustering, a hierarchical
  clustering approach which uses a linkage criteria in order to successively merge
  similar clusters until a desired intracluster distance threshold or number of
  clusters is reached. 
  \begin{itemize}
   	\item We used the Ward linkage criteria, which works to minimize the sum of
   	the squared differences within all clusters.
   	\item We elected to choose the number of clusters rather than the distance
   	threshold.
   	\item For our data, non-parameteric methods such as Bayesian Gaussian mixture
   	models tend to delocalize the clusters in parameter space (see Supporting
   	Information).
   	%BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so it's tails are on both sides of the center cluster.
  \end{itemize}

  % BJC2: this part may expand a bit if I try different clustering approaches. But
  % this is the one I'm going with for now.
  We clustered based on the two diagonal entries of $A$ and the two diagonal entries 
  of $\Sigma$.
  \begin{itemize}
   \item One can choose alternative clustering features, such as the eigenvalues of
   the $A$ and $\Sigma$ matrices, but we chose their diagonals because they can be
   easily translated to solute behavior.
   \item We also chose to cluster the diagonals of each matrix independently before
   combining the clusters to assign final state labels. 
   \item If we divide the total states into $m$ clusters based on the diagonal entries
   of $A$ and, separately, $n$ clusters based on the diagonal entries of $\Sigma$,
   then there are a total of $mn$ possible cluster combinations.
   \item This allows slightly more flexibility in the total number of states compared
   to clustering on all four features at once, since there can be up to, but not 
   necessarily exactly, $mn$ states. 
  \end{itemize}

  Choosing the number of clusters can be somewhat subjective so
  we attempted to add some structure to the selection process by following
  a set of qualitative and quantitative guidelines.
  \begin{itemize}
  	%BJC3: not sure if the commented point worth making.
%    \item We should expect a relatively high number of states. If we only consider
%    the diagonal entries of the $A$ and $\Sigma$ matrices, a total of four independent
%    variables, we can consider clustering each into at least two groups (higher versus
%    lower values), which implies $2^4$ distinct dynamical behaviors. 
    \item We used the Silhouette test in order to score the quality of
    clusters as a function of the number of clusters chosen.
    \item For our data, the Silhouette test generally favors the lowest number
    of clusters possible (see Supporting Information).
    \item However, choosing too few clusters tends to result in 
    inadequate distinguishment between visually obvious differences in 
    dynamic behavior.
    \item This results in finalized parameter sets that are averages of
    distinct behavior which presents further problems with the predictive
    modeling that we discuss later on.
    \item We aimed to maintain the highest Silhouette score, and thus lowest
    number of clusters, possible while verifying that visually distinct 
    states stayed separated.
    \item Based on these guidelines, we decided to group the $A$ and $\Sigma$
    parameters into five clusters each. 
	\item Of the 25 distinct states allowed by this formulation, the solutes
	in this study clustered into 13--18 distinct clusters.
  \end{itemize}

@@

  We used the parameter inference component of the IHMM algorithm in order to 
  infer $A$ and $\Sigma$ of the clustered states.
  \begin{itemize}
   %BJC2: I'm unsure of the precise reasoning here.
   \item We could not simply take the mean of the clustered 
   $A$ and $\mathbf{e}_t$ parameters because it is not clear that this is a linear 
   operation for this problem. 
   \item To circumvent this problem, we modified the ($r$, $z$) solute
   trajectories so that they had a mean of zero, leaving only the 
   fluctations. 
   \item We did this by subtracting the maximum likelihood estimate
   of the $\mathbf{c}$ vector from each same-state segement of the unclustered
   trajectory.   
   \item We used the IHMM algorithm on this modified trajectory to infer
   the clustered state parameters by fixing the clustered state sequence. 
  \end{itemize}

@@

  \section{Results and Discussion}

  Solutes in this system show a wide range of behavior influenced by the 
  heterogeneity of the membrane's nanostructure as well as the interactions 
  between monomer and solute chemical functionality. 
  \begin{itemize}  
  	\item Our application of the IHMM does a good job of identifying and
  	distinguishing these behaviors.   	
  	\item Clustering the behaviors helps us to tell a coherent story which
  	emphasizes those interactions which most heavily influence solute transport.
  	\item This analysis approach helps us to break down the very complex behavior
  	exhibited by solutes over long MD trajectories into discrete categories.
  \end{itemize}

  \subsection{Automatic Detection of Distinct Dynamical Modes}\label{section:find_modes}

  %BJC3: I'm not sure if it's worth talking about all of the solutes in this section.
  % there is a lot to talk about just with methanol (which is all I've done for now -- wanted to
  % get feedback on analysis approach).
  %BJC3: I see this more as a demonstration of the model. I think this work has higher
  % impact potential so I don't want it to be 15 pages.
  %BJC3: Although, it might be a good idea to include Urea or Acetic acid as a second example
  % molecule because their behavior is pretty different since their carbonyl group tend to 
  % associate with sodium a lot.

  %BJC3: obviously can use a better thesis.
  We showcase this modeling approach by example. 
  \begin{itemize}
    \item In Figure~\ref{fig:mechanism_map}, we plot a representative 2D methanol 
    trajectory in cylindrical coordinates.
    \item The coordinates are colored according to the cluster with which methanol's
    dynamics are most consistent, which implies that this particular methanol 
    trajctory exhibits 6 distinct dynamical behaviors. 
    \item The solute timeseries are coupled with color coded bars which describe the
    solute's local environment and physical interactions that it undergoes at that
    time frame.
    \item From the top, they describe whether the solute is associated with sodium,
    whether the solute is hydrogen bonding with the monomer as well as what part of
    the monomer it is hydrogen bonding to, the local number density surrounding the
    solute and the radial location of the solute with respect to the nearest pore
    center (this information is redundant but can be a useful visual aid). %BJC3: still debating removing that bar
  \end{itemize}

  %BJC3: I still need labels for this plot
  \begin{figure}
  \includegraphics[width=\textwidth]{mechanism_map.pdf}
  \caption{}\label{fig:mechanism_map}
  \end{figure}

  One can gain significant chemical intuition just by studying plots like
  Figure~\ref{fig:mechanism_map}.
  \begin{itemize}
    \item It is clear that, for methanol, association with sodium is a much rarer
    interaction than hydrogen bonding with the LLC monomers.
    \item Methanol hydrogen bonds to all regions of the monomers dependent on
    its radial position.
    \item Its fluctuations tend to be smallest when hydrogen bonded or in areas
    of high local number density. 
    \item For example, from approximately 75 to 525 ns, methanol appears to be trapped
    in a high density region of the tails.
    \item In the time that follows, it enters a region of relatively low density
    where fluctuations are quite large. 
    \item During this time period, there is intermittent, short-lived hydrogen 
    bonding with the oxygen atoms at the tail ends, as suggested by the frequent 
    state changes during that time period and red slivers in the bar above.
  \end{itemize}

  %BJC3: I think I'll just skip to the clustered results. I'd like to keep this
  % paper on the shorter side.
%  The IHMM does a sufficient job of capturing differences in solute dynamics
%  for individual trajectories.
%  \begin{itemize}
%    \item In Figure TBD, we show the states identified by the IHMM for a single
%    methanol trajectory. The IHMM found x number of states.
%  \end{itemize}

%  Depending on the path followed, solute trajectories show diverse behavior.
%  \begin{itemize}
%    \item Some show lots of movement
%    \item Some show almost no movement
%    \item While all trajectories might not be the same, it is likely that 
%    multiple trajectories might share some similar behavior.
%  \end{itemize}

  We may learn the most by studying the dynamical modes common to the majority of 
  the solute trajectories.
  \begin{itemize}
    \item Using the IHMM, we identified 13 total dynamical modes exhibited by 
    methanol. 
    \item Of those, 4 appear in at least 50 \% of the methanol trajectories, and
    2 of them appear in over 90 \% of the methanol trajectories.
    \item In Figure~\ref{fig:common_states_MET_lines}, we plot representative dynamics
    of each of the 4 prevelant states.
    \item Based on their self-transition probabilities, we estimated the average 
    time spent by each solute in each state (Figure~\ref{fig:dwell_times_MET}).
    \item States 2 and 4 have long dwell times relative to states 1 and 3 because
    they have high self-transition probabilities.
    \item States 1 and 3 show large fluctuations relative to the other states owing
    to larger covariances in both the axial and radial dimensions. (Figure~\ref{fig:A_sigma_scatter_MET})
    \item States 1 and 2 have lower autoregressive coefficients relative to states
    3 and 4.
    \item All of these states are present in Figure~\ref{fig:mechanism_map} and colored
    accordingly.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.6\textwidth}
  \includegraphics[width=\textwidth]{common_states_MET.pdf}
  \caption{}\label{fig:common_states_MET_lines}
  \end{subfigure}
  \begin{subfigure}{0.35\textwidth}
  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}
  \caption{}\label{fig:dwell_times_MET}
  \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
  \caption{}\label{fig:A_sigma_scatter_MET}
  \end{subfigure}
  \caption{}\label{fig:common_states_MET}
  \end{figure}

  %BJC3: I'm struggling a bit with this part of the analysis. The story isn't as clear
  % cut as I want because it seems like states which contribute to the same cluster behave
  % the way they do for somewhat varied reasons. Hence the short paragraph after this one.
  We can attempt to understand the behavior described in Figure~\ref{fig:common_states_MET}
  further by relating them to their interactions with the membrane. 
  \begin{itemize}
    \item It is clear that solutes can behave similar in different regions of the 
    membrane because each state hydrogen bonds with LLC atoms located from the monomer head
    groups to the tails. 
    %BJC3: The following is a hypothesis to be tested.
    \item The key difference is the lifetime of these interactions. 
    \item When in a trapped state (one with smaller covariance like 2 and 4), hydrogen bond
    lifetimes are generally longer.
    \item While hydrogen bonds occur in states 1 and 3, the lifetimes are shorter, perhaps
    broken by fluctuations in their local environment.
  \end{itemize}

  It is important to understand that the clustered parameter sets are
  essentially summaries of many related behaviors. Therefore, the most thorough
  understanding of a specific segment will be gained using descriptive visualizations
  like Figure~\ref{fig:mechanism_map}. But this model very clearly tells the user where
  to look.
  %BJC3: could do a case study of sorts on a chosen segment

  %BJC3: this figure is not even close to done
  %BJC3: I've tried a couple different things to look at the hbonds. The other was 
  % how often they are hydrogen bonded in general versus not hydrogen bond. They all
  % hydrogen bond about the same amount. So I think hbond lifetimes may be the key. 
  % I need to implement this first to test that hypothesis.
  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
  \caption{}\label{fig:hbond_pichart}
  \end{figure}

@@

  We can use the IHMM in order to generate stochastic trajectory realizations
  which bear qualitatively similar characteristics to those output
  by our MD simulations.
  \begin{itemize}
    \item Because we clustered the data, we are left with a single transition
    probability matrix which allows transitions between dynamical behaviors
    shared by the 24 MD trajectories.
    \item Therefore, the realizations generated by our model are representative
    of the average behavior of solutes studied.
    \item In Figure~\ref{fig:trajectory_realizations_MET}, we show some stochastic
    realizations generated by our models compared directly to MD.
    \item The trajectories show clear periods of entrapment with intermittent hops.
  \end{itemize}

  % BJC3: It might be good to show a few MD trajectories since they vary somewhat widely
  % in behavior.
  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
  \caption{}\label{fig:trajectory_realizations_MET}
  \end{figure}

  \noindent The MSDs calculated by stochastic realizations of our model are
  quantitatively similar to MD.
  \begin{itemize}
  	\item For all solutes except acetic acid, our predicted MSD curve lie close to
  	but below the 1$\sigma$ confidence intervals of MD.
  	\item However, in these cases, the average MD MSDs are driven up by single trajectories
    with uncharacteristically large MSDs.
    \item If we remove these uncharacteristic trajectories, the agreement between 
    MD and our realizations improves. 
    % BJC3: I'm not sure the best course of action. I've double checked the bootstrapping
    % procedure and it make sense to me.
    % BJC3: I could show how it's possible to get good agreeement with MD by only
    % generating 24 solute trajectories since in some cases, outliers heavily weight the averages.
    \item Acetic acid has no obvious outliers and shows good agreement between MD and
    IHMM realizations.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_MET.pdf}
  \caption{}\label{fig:msd_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_GCL.pdf}
  \caption{}\label{fig:msd_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_URE.pdf}
  \caption{}\label{fig:msd_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_ACH.pdf}
  \caption{}\label{fig:msd_ACH}
  \end{subfigure}
  \end{figure}

  % BJC3: maybe need to talk about the curvature. Our model shouldn't have noticeable
  % curvature because it's only correlated with one step

@@

  %BJC3: I still need to implement this into my mean first passage time code, but it will very closely follow the 
  % methodology of the last paper. However, if I see that the decay in flux is
  % near 2 (which I expect), then I may add a short section showing how you can
  % simply use the ratio of the MSD slopes in order to estimate selectivity.
  % I think they should give the same results. Haven't tested it yet though.

  We can use realizations of our model in order to predict macropscopic flux and
  selectivity.
  \begin{itemize}
    \item For various length pores, we constructed distributions of first passage times for each solute and
    fit them to Equation~\ref{eqn:passage_times} in order estimate the mean 
    first passage time (MFPT). 
    \item We plotted the inverse of MFPT, the solute flux, versus pore length
    in Figure TBD.
    \item Flux rapdily decays with pore length.
    \item Selectivity is simply the ratio of the fluxes for this system.
  \end{itemize}

  %BJC3: this paragraph is speculative.
  We can use the slopes of the MSD curves to estimate selectivity in a simpler way.
  \begin{itemize}
  	\item As in our previous work, we fit the flux curves to a decaying power law function
  	of the form:
  	\begin{equation}
    	Ae^{-\beta}
  	\end{equation}
  	\item We find that in all cases, $\beta$ is equal to 2. This is consistent with Brownian
	motion which implies long term linear behavior of the MSD curves. 
	\item Since the diffusion constant is linearly proportional to the slope of the MSD, and 
	selectivity in this system can be estimated as the ratio of diffusion constants, we can 
	estimate selectivity directly based on the slopes of our stochastically simulated MSD curves.
  \end{itemize}

@@

  \noindent We showcase this modeling approach by example, but it is important to
  recognize the generality of this analysis.

@@

  \noindent We show how one can use the IHMM to predict macroscopic transport properties. \\
